Some notes on quasinormal mode tests

### 2021-08-31 notes/hector_qnms/qnms.tex
HS: upd theory specific list with EFTofGR
HS: added Einstein-Aether paper reference

\documentclass[aps,10pt,preprint,
               notitlepage,onecolumn,superscriptaddress,
               eqsecnum,
               nofootinbib,tightenlines,floatfix]{revtex4-1}

@@

\begin{itemize}
    \item Einstein-dilaton-Gauss-Bonnet -- (NR)~\cite{Blazquez-Salcedo:2016enn},
        (SR)~\cite{Pierini:2021jxd}.~\hs{Having results at both NR and SR approximations
        could be useful to assess {\sc parSpec} truncated at different spin-orders};
    \item dynamical Chern-Simons -- (NR)~\cite{Molina:2010fb}, (SR)~\cite{Wagle:2021tam,Srivastava:2021imr};
    \item Einstein-Maxwell-dilaton -- (NR)~\cite{Ferrari:1984zz}, (SR)~\cite{Brito:2018hjh};
\end{itemize}

>>>>

\documentclass[aps,prd,10pt,preprint,
               notitlepage,onecolumn,superscriptaddress,
               eqsecnum,
               nofootinbib,tightenlines,floatfix]{revtex4-2}

@@

\begin{itemize}
    \item Einstein-dilaton-Gauss-Bonnet -- (NR)~\cite{Blazquez-Salcedo:2016enn},
        (SR)~\cite{Pierini:2021jxd}.~\hs{Having results at both NR and SR approximations
        could be useful to assess {\sc parSpec} truncated at different spin-orders}.
    \item dynamical Chern-Simons -- (NR)~\cite{Molina:2010fb}, (SR)~\cite{Wagle:2021tam,Srivastava:2021imr}.
    \item Einstein-Maxwell-dilaton -- (NR)~\cite{Ferrari:1984zz}, (SR)~\cite{Brito:2018hjh}.
    \item EFTofGR -- (NR, cubic)~\cite{deRham:2020ejn} and (NR, quadratic)~\cite{Cardoso:2018ptl}.
    \item Einstein-Aether -- (NR, odd/axial parity)~\cite{Tsujikawa:2021typ}. Analysis of quadratic Lagrangian only; no mode calculation.
\end{itemize}
